A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-08-01 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: SIC-POVM figure
Added a figure to illustrate a SIC-POVM on the Bloch ball, which is a tetrahedron inside the ball.
Alternatively, one could define a tetrahedron that fits the ball inside, which is illustrated in a separate subfigure.
There is not enough space on the figure to label all the extreme points as was done here:
https://commons.wikimedia.org/wiki/File:Regular_tetrahedron_inscribed_in_a_sphere.svg
The text would be too small.
I left the labels as comments anyway.

>>>>

	% perspective
	% from scipy.spatial.transform import Rotation as R
	% R.from_euler("yx", [50, 10], degrees=True).as_euler("xyz", degrees=True).round(0)[::-1]
	\newcommand{\yaw}{12}
	\newcommand{\pitch}{49}
	\newcommand{\roll}{15}

	\newcommand{\radius}{1}

	\begin{subfigure}[c]{0.23\textwidth}
		\centering
		\begin{tikzpicture}[x={(\xx cm, \xy cm)}, y={(\yx cm, \yy cm)}, z={(\zx cm, \zy cm)}, scale=1.2]
			% Bloch sphere (outline drawn in canvas plane)
			\draw (0, 0, 0) circle (\radius cm);

			% tetrahedron
			\coordinate (A) at (0, 1, 0);
			\coordinate (B) at (0, -1/3, {sqrt(8/9)});
			\coordinate (C) at ({sqrt(2/3)}, -1/3, {-sqrt(2/9)});
			\coordinate (D) at ({-sqrt(2/3)}, -1/3, {-sqrt(2/9)});
			\begin{scope}[every node/.style={font=\tiny}]
				\draw (A) -- (B) -- (C) -- cycle;
				\draw (A) -- (B) -- (D) -- cycle;
				\draw (A) -- (C) -- (D) -- cycle;
				\draw (B) -- (C) -- (D) -- cycle;
%				\shadedraw (A) circle (0.03 cm) node[above] {$| 0 \rangle$};
%				\shadedraw (B) circle (0.03 cm) node[below] {$\frac{1}{\sqrt{3}} | 0 \rangle + \sqrt{\frac{2}{3}} e^{i\frac{2\pi}{3}} | 1 \rangle$};
%				\shadedraw (C) circle (0.03 cm) node[above] {$\frac{1}{\sqrt{3}} | 0 \rangle + \sqrt{\frac{2}{3}} e^{i\frac{4\pi}{3}} | 1 \rangle$};
%				\shadedraw (D) circle (0.03 cm) node[below] {$\frac{1}{\sqrt{3}} | 0 \rangle + \sqrt{\frac{2}{3}} | 1 \rangle$};
			\end{scope}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\begin{subfigure}[c]{0.23\textwidth}
		\centering
		\begin{tikzpicture}[x={(\xx cm, \xy cm)}, y={(\yx cm, \yy cm)}, z={(\zx cm, \zy cm)}, scale=0.65]
			% Bloch sphere (outline drawn in canvas plane)
			\draw (0, 0, 0) circle (\radius cm);

			% inscribed tetrahedron
			\begin{scope}[scale=3, every node/.style={font=\small}]
				\coordinate (A) at (0, 1, 0);
				\coordinate (B) at (0, -1/3, {sqrt(8/9)});
				\coordinate (C) at ({sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\coordinate (D) at ({-sqrt(2/3)}, -1/3, {-sqrt(2/9)});
				\draw (A) -- (B) -- (C) -- cycle;
				\draw (A) -- (B) -- (D) -- cycle;
				\draw (A) -- (C) -- (D) -- cycle;
				\draw (B) -- (C) -- (D) -- cycle;
			\end{scope}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\caption{(a) Example of a SIC-POVM on a Bloch ball. The four extreme points of the tetrahedron represent the states $P_i$. States with positive $\lambda_i$ lie within the tetrahedron, while all other states require negative coefficients. (b) The Bloch ball can alternatively be circumscribed by a larger tetrahedron to guarantee positive coefficients, but the extreme points are no longer physical states.}
\end{figure}
